Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/discussion.tex
working on discussion

% !TEX root = ../paper.tex
\section{Discussion}

% noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

% tuning the F score for precision and recall
Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.

% examples.
In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
due to the same word being used in a different context.
For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
better code generation with GCC at least.''}
This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing. However, it is classified as a useful comment. This may be caused by the word \emph{generate} which appears in both documents.

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

@@

%\subsection{Binary Classification}

Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

\subsection{Threat to Validity}

>>>>

% !TEX root = ../paper.tex
\section{Discussion}
Our results have shown that using semantic similarity can classify usefulness of comments and our approach also can reduce human effort ant error prone of manual classification. Besides the results, we also found interesting findings in our case study. We discuss these findings as follows:

% tuning the F score for precision and recall
%Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
%For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
%If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.

% examples.
\subsection{What kind of comments cannot be classified using semantic similarity?}
From the results of RQ1, we found that some comments were not determined by our models. Specifically, we were interested in comments with useful class (\texttt{YES} = 3) and useless class (\texttt{YES} = 0). To investigate the reason behind this, we examined these comments. We found that .....

%In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
%due to the same word being used in a different context.
%For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
%better code generation with GCC at least.''}
%This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing. However, it is classified as a useful comment. This may be caused by the word \emph{generate} which appears in both documents.

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
\subsection*{What decisions are made during the manual classification?}
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

@@

\subsection*{Threat to Validity}
\indent \textbf{Internal Valdity:} % noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score. \\
\indent \textbf{External Validity:} \\
